% !TeX spellcheck = en_US
%# -*- coding: utf-8-unix -*-
%%==================================================
%% abstract.tex for SJTU Master Thesis
%%==================================================

\begin{abstract}

最近几年，互联网上的视觉数据呈现爆炸式的发展，如何快速有效的检索这些数据，是一项迫在眉睫的重要挑战。为了解决这个问题，基于哈希的近似最近邻检索以其在计算速度和存储上的进步，受到了各方面的关注。
其中，局部敏感哈希是一种广为人知的非数据驱动的哈希技术。其使用随机超平面来划分空间构造哈希函数。在局部敏感哈希之后，许多数据驱动的哈希技术被提出.这些方法都是用超平面来划分空间构造哈希函数。
与此同时，其他的一些非线性的哈希也被提出，例如球哈希和K均值哈希。这些哈希技术不基于超平面，而采用非线性的哈希函数，从而相比于线性哈希有更强的划分空间的能力。
尽管上述哈希方法取得了很好的哈希效果，但仍然存在两个重要的缺陷。首先，对于大数据应用，数据存储在分布式硬盘群组中，无法同时读入计算机内存，也就无法采用上述的哈希方法进行处理。第二，互联网中的很多数据以流数据的形式存在，而上述哈希算法需要同时获取全部数据进行处理。
为了解决这些问题，在线哈希技术的概念被提出。在线哈希旨在解决了上述的两个问题，但是，目前存在的在线哈希都是线性哈希技术，相比于非线性哈希方法，效果有所逊色。如何将在线哈希技术与非线性哈希技术相结合成为了热点。
最近，神经网络良好的非线性特征提取能力受到了广泛关注，其有效性得到了很多比赛和真实应用的验证。将神经网络与在线哈希技术相结合，为上述问题打开了新的突破方向。神经网络类型多样，受限玻尔兹曼机，卷积网络，深度信念网络，自组织映射网络等网络模型，各有其在不同任务上的优势。在本篇论文中，我们探索了多种神经网络在哈希任务上的应用方法。同时，提出了在线自组织哈希这一创新的方法。

\keywords{\large 哈希 \quad 在线学习 \quad 神经网络}
\end{abstract}

\begin{englishabstract}

An imperial edict issued in 1896 by Emperor Guangxu, established Nanyang Public School in Shanghai. The normal school, school of foreign studies, middle school and a high school were established. Sheng Xuanhuai, the person responsible for proposing the idea to the emperor, became the first president and is regarded as the founder of the university.

During the 1930s, the university gained a reputation of nurturing top engineers. After the foundation of People's Republic, some faculties were transferred to other universities. A significant amount of its faculty were sent in 1956, by the national government, to Xi'an to help build up Xi'an Jiao Tong University in western China. Afterwards, the school was officially renamed Shanghai Jiao Tong University.

Since the reform and opening up policy in China, SJTU has taken the lead in management reform of institutions for higher education, regaining its vigor and vitality with an unprecedented momentum of growth. SJTU includes five beautiful campuses, Xuhui, Minhang, Luwan Qibao, and Fahua, taking up an area of about 3,225,833 m2. A number of disciplines have been advancing towards the top echelon internationally, and a batch of burgeoning branches of learning have taken an important position domestically.

Today SJTU has 31 schools (departments), 63 undergraduate programs, 250 masters-degree programs, 203 Ph.D. programs, 28 post-doctorate programs, and 11 state key laboratories and national engineering research centers.

SJTU boasts a large number of famous scientists and professors, including 35 academics of the Academy of Sciences and Academy of Engineering, 95 accredited professors and chair professors of the "Cheung Kong Scholars Program" and more than 2,000 professors and associate professors.

Its total enrollment of students amounts to 35,929, of which 1,564 are international students. There are 16,802 undergraduates, and 17,563 masters and Ph.D. candidates. After more than a century of operation, Jiao Tong University has inherited the old tradition of "high starting points, solid foundation, strict requirements and extensive practice." Students from SJTU have won top prizes in various competitions, including ACM International Collegiate Programming Contest, International Mathematical Contest in Modeling and Electronics Design Contests. Famous alumni include Jiang Zemin, Lu Dingyi, Ding Guangen, Wang Daohan, Qian Xuesen, Wu Wenjun, Zou Taofen, Mao Yisheng, Cai Er, Huang Yanpei, Shao Lizi, Wang An and many more. More than 200 of the academics of the Chinese Academy of Sciences and Chinese Academy of Engineering are alumni of Jiao Tong University.

\englishkeywords{\large SJTU, master thesis, XeTeX/LaTeX template}
\end{englishabstract}

